An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-17 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@

 \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} 
interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. 
Given the correctness specification $\sigma$, the {\sc Synthesize} procedure 
tries to find an existential witness $\vec{F}$ satisfying the specification 
$\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). 
If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution 
(i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify} 
with a lower bound (that is incremented during every iteration), in order to check whether it is a proper solution 
({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). 
If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment 
with the lowest cost; otherwise, in the CEGIS traditional method, additional information is 
provided to the phase {\sc synthesize}, in the form of a new counterexample that is added 
to the {\sc inputs} set and the loop iterates again; however, in our variant CEGIS method, 
if the {\sc verify} phase is not successful, then a new candidate is generated by {\sc synthesize} 
and the lower bound in incremented in order to pursuit the lowest cost.
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%

 \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
One may notice that each iteration of the CEGIS loop adds a new input to the finite set 
$\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ 
is finite because we use bit-vector expressions, this means that the refinement loop can 
only iterate over a finite number of times; however, {\sc synthesize} may conclude that 
no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ 
exists and our synthesis engine can then conclude that no feasible equipment combination was found.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

\textcolor{red}{In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.}

One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.

\textcolor{red}{However, in our variant CEGIS method proposed at this paper, there are four particular differences related to traditional CEGIS: (1) there is not test vectors and every candidate is generated during the run-time at the {\sc Synthesize} phase and sent to {\sc Verify} phase; (2) if the {\sc Verify} phase is not successful, then a new candidate is generated by {\sc Synthesize} and (3) the lower bound of {\sc Verify} phase is incremented in order to pursuit the lowest cost; (4) therefore, there is not the refinement from the {\sc Verify} back to {\sc Synthesize} phase (a new counterexample is not added to the {\sc inputs} set) because a FAIL during {\sc Verify} just discard the candidate, that can be feasible in the next iteration with a new lower bound.}
